Apache Flink\texttrademark: Unified Stream and Batch Processing \\ in a Single Engine

### 2015-11-30 batch.tex
autoref not ref
Updates from ShareLaTeX

\subsection{Query Optimization}

Flink’s optimizer builds on techniques from parallel database systems such as plan equivalence, cost modeling and interesting property propagation. However, the arbitrary UDF-heavy DAGs that make up Flink’s dataflow programs do not allow a traditional optimizer to employ database techniques out of the box \cite{blackBoxes}, since the operators hide their semantics from the optimizer. For the same reason, cardinality and cost estimation methods are equally difficult to employ. Flink’s runtime supports various execution strategies including repartition/broadcast data transfer, as well as sort-based grouping and sort- and hash-based join implementations. Flink’s optimizer enumerates different physical plans based on the concept of interesting properties propagation \cite{scopeOptimizer}, using a cost-based approach to choose among multiple physical plans. The cost includes network/disk I/O and CPU cost. To overcome the cardinality estimation issues that were mentioned earlier,  Flink’s optimizer uses hints that are provided by the programmer.

>>>>

\subsection{Query Optimization} 
Flink’s optimizer builds on techniques from parallel database systems such as plan equivalence, cost modeling and interesting property propagation. However, the arbitrary UDF-heavy DAGs that make up Flink’s dataflow programs do not allow a traditional optimizer to employ database techniques out of the box \cite{blackBoxes}, since the operators hide their semantics from the optimizer. For the same reason, cardinality and cost estimation methods are equally difficult to employ. Flink’s runtime supports various execution strategies including repartition/broadcast data transfer, as well as sort-based grouping and sort- and hash-based join implementations. Flink’s optimizer enumerates different physical plans based on the concept of interesting properties propagation \cite{scopeOptimizer}, using a cost-based approach to choose among multiple physical plans. The cost includes network/disk I/O and CPU cost. To overcome the cardinality estimation issues that were mentioned earlier,  Flink’s optimizer uses hints that are provided by the programmer.
